Homicide Increases in the COVID-19 Era

### 2025-02-20 Draft1.qmd
fixed error - crime_la is already combined in initial block now

# Combine the datasets
crime_la <- rbind(crime_rate_ds, crime_old_ds)

# Remove missing values and empty strings in Vict.Sex column
crime_la <- subset(crime_la, Vict.Sex != "" & !is.na(Vict.Sex))

>>>>

```{r}
# Remove missing values and empty strings in Vict.Sex column
crime_la <- subset(crime_la, Vict.Sex != "" & !is.na(Vict.Sex))
